
\begin{bio}
  {\bfseries Chung-Chi Chen} is a postdoctoral researcher at the MOST Joint Research Center for AI Technology and All Vista Healthcare, Taiwan. He got the Ph.D. degree in the Department of Computer Science and Information Engineering at Na- tional Taiwan University. He received the M.S. degree in Quantitative Finance from National Tsing Hua University, Taiwan. His research focuses on opinion mining and sentiment analysis in finance. He is the organizer of FinNum shared task series in NTCIR (2018-2022) and the FinNLP workshop series in IJCAI (2019-2021). He is the presenter of the AACL-2020 ``Natural Language Processing in Financial Technology Applications''  tutorial and the presenter of the EMNLP-2021 ``Financial Opinion Mining'' tutorial. His work has been published in ACL, WWW, SIGIR, IJCAI, and CIKM, and served as PC members in ACL, AAAI, EMNLP, CIKM, and WSDM. He won the 1st prize in both the Jih Sun FinTech Hackathon (2019) and the Standard Chartered FinTech competition (2018), and the 2nd prize in both the Jih Sun FinTech Hackathon (2018) and the E.SUN FHC FinTech Hackathon (2017).

  {\bfseries Hen-Hsen Huang} is an assistant research fellow at the Institue of Information Science, Academia Sinica, Taiwan. His research interests include natural language processing and information retrieval. His work has been published in ACL, SI- GIR, WWW, IJCAI, CIKM, COLING, and so on. Dr. Huang received the Honorable Mention of Doctoral Dissertation Award of ACLCLP in 2014 and the Honorable Mention of Master Thesis Award of ACLCLP in 2008. He served as the registration chair of TAAI 2017, the publication chair of ROCLING 2020, and as PC members of representative conferences in computational linguistics including ACL, COLING, EMNLP, and NAACL. He was one of organizers of FinNum Task at NTCIR and FinNLP Workshop at IJCAI.

  {\bfseries Hsin-Hsi Chen} is a professor in the Department of Computer Science and Information Engineering, National Taiwan University. He was conference chair of IJCNLP 2013, program co-chair of ACM SIGIR 2010, senior PC member of ACM SIGIR 2006, 2007, 2008 and 2009, area/track chair of AAAI 2020, EMNLP 2018, ACL 2012, ACL-IJCNLP 2009 and ACM CIKM 2008, and PC member of many conferences (IJCAI, SIGIR, WSDM, ACL, COLING, EMNLP, NAACL, EACL, IJCNLP, WWW, and so on). He will be conference chair of ACM SIGIR 2023. He received Google research awards in 2007 and 2012, MOST Outstanding Research Award in 2017, and the AmTRAN Chair Professorship in 2018.

\end{bio}

\begin{tutorial}
  {Financial Opinion Mining}
  {Hsin-Hsi Chen, Hen-Hsen Huang, Chung-Chi Chen}}
  {\daydateyear, \tutorialmorningtime}


In this tutorial, we disassemble a financial opinion into 12 components. This tutorial starts by introducing the components one by one and introduces the related studies from both NLP technical aspects and the real-world applications. Besides, in the FinTech trend, financial service gets much attention from the financial industry. However, few studies discuss the opinion toward financial service. In this tutorial, we will also introduce this kind of opinion and provide a comparison with the opinion of investors and customer's opinions in other industries. Several unexplored research questions will be proposed. The audiences of this tutorial will gain an overview of financial opinion mining and figure out their research directions based on the proposed research agenda.

\end{tutorial}
