\section{Message from the General Chair}\vspace{2em}
\setheaders%
    {Message from the General Chair}%
    {Message from the General Chair}
\thispagestyle{emptyheader}

\setlength{\parskip}{1ex}

EMNLP 2021 is one of the first hybrid conferences in the field of natural language processing. It is also for us, the organizing team, uncharted domain. Organizing a hybrid conference has felt like organizing two conferences, a virtual one and an in-person one, which seamlessly must work together and with a kind of multi-task objective make the conference experience synergistic and successful both remotely and in person. With this challenge come opportunities. The hybrid format allows remote participation in a conference that is held onsite in Punta Cana, The Dominican Republic, and allows creating a real conference feeling for those who do not want to travel the many miles from the other side of the world and increase their carbon footprint, and for those who have budget restrictions for traveling. We welcome you all!

As in previous years, the purpose of the General Chair’s preface is to express thanks to the amazing team of organizing chairs whose heroic efforts made this hybrid conference possible. The organizing team includes:

\begin{itemize}

\item The Programme Chairs -- Xuanjing Huang, Lucia Specia and Scott Yih -- who did a tremendous job to manage the reviewing process and set up an outstanding scientific program.
\item The Senior Area Chairs, Area Chairs and Reviewers whose expertise enabled authors to learn from their reviews and to deliver papers that improved on their original submissions.
\item The Demonstration Chairs -- Heike Adel and Shuming Shi -- who selected outstanding demonstrations to complement the program of the main conference.
\item The Workshop Chairs -- Minlie Huang and Parisa Kordjamshidi -- who made a huge effort for organizing hybrid workshops and satellite conferences.
\item The Publication Chairs -- Loic Barrault, Greg Durrett and Yansong Feng -- who met the challenge of identifying and correcting the myriad ways in which papers could be wrongly formatted, and who assembled the result into the conference proceedings.
\item The Handbook Chair -- Els Lefever -- for the timely delivery of handbook information.
\item The Publication Chairs of Findings -- Gabriel Stanovsky and Tim Van de Cruys -- who made it possible that many interesting papers and their findings can be accessed and cited by the public.
\item The Tutorial Chairs -- Jing Jiang and Ivan Vulic -- who selected six excellent tutorials to be presented at the conference.
\item The Ethics Chairs -- Margot Mieskes and Christopher Potts -- who undertook the delicate task of checking papers that had been flagged for potential ethical issues.
\item The Website Chair -- Miryam de Lhoneux -- who ensured that the EMNLP 2021 website promoting this hybrid conference stayed up to date; Mingxiao Li who offered website support; and Nathan Cornille who was responsible for the graphical designs.
\item The Virtual Infrastructure Chairs -- Quinh Do, Zhaopeng Tu and Dani Yogatama -- and the Underline team -- Sol Rosenberg, Daniel Luise, Jernej Masnec, Luka Simic, Alexandru Pricop and various support staff.
\item The Volunteer Coordinators and Scholarship Chairs -- Qi Wu and Diyi Yang -- who managed to attract over 200 student and early career volunteers willing to make EMNLP 2021 a success.
\item The Publicity Chairs -- Raffaella Bernardi and Preethi Jyothi -- who have served as both the voice of EMNLP 2021 in communicating with the community and as its ears, reporting on community concerns as soon as they were expressed.
\item The Diversity & Inclusion Chairs -- Laura Alonso Alemany and Toshiaki Nakazawa -- who have worked tirelessly to make EMNLP 2021 as welcoming and inclusive as possible for all participants. They have worked with community members to create Birds of a Feather sessions, Affinity Group sessions, student panels and mentoring sessions which contribute to reinforcing the EMNLP community (and sub-groups within this community).
\end{itemize}

We also want to express special thanks to Priscilla Rasmussen, the ACL Business Manager, first for booking EMNLP 2021 into a beautiful resort in the Dominican Republic, and for the local organization of a hybrid conference. Many thanks, Priscilla!

Finally, we would like to express gratitude to our sponsors, whose generous support has been invaluable in building up EMNLP 2021 to what it is now. These include the Diamond-level sponsors -- Apple, Bloomberg Engineering, Facebook AI and Google Research; the Platinum-level sponsors -- Amazon Science, Baidu, ByteDance, DeepMind, G Research and Megagon Labs; the Gold-level sponsors -- Grammarly and Microsoft; the Silver-level sponsors -- duolingo, Naver and Naver Labs Europe; the Bronze-level sponsors -- Adobe, Babelscape, human language technology center of excellence and LegalForce; and the Supporter servicenow. I would like to thank the Diversity and Inclusion Champion sponsors -- Amazon Science, Deepmind, Google Research and Microsoft; the Diversity and Inclusion Ally sponsor -- Morgan Stanley; and the Diversity and Inclusion Contributor sponsors -- Adobe and IBM. ACL SIGDAT has also generously contributed to supporting scholarships for attending the conference.

\vspace{3em}

\noindent \textit{Marie-Francine Moens}, KU Leuven, Belgium \\
\noindent EMNLP 2021 General Chair \\

\index{Moens, Marie-Francine}
